Nope

### 2010-12-14 AffineLieAlgebras/MQFT2010/article.tex
Reference to Bernstein 1971 fixed

To show this we use the recursive approach to branching presented in [our
preprint] (similar to the one used in \cite{ilyin812pbc} for maximal
embeddings). We consider the subalgebra $\frak{a}$ together with its
counterpart $\frak{a}_{\bot }$ ''orthogonal'' to $\frak{a}$ with respect to
the Killing form and also $\widetilde{\frak{a}_{\perp }}:=\frak{a}_{\perp
}\oplus \frak{h}_{\perp }$ where $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus 
\frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$. For any reductive
algebra $\frak{a}$ the subalgebra $\frak{a}_{\bot }\hookrightarrow \frak{g}$
is regular and reductive. For a highest weight integrable module $L^{\left(
\mu \right) }$ and orthogonal pair of subalgebras $\left( \frak{a},\frak{a}%
_{\bot }\right) $ we consider the singular element $\Psi ^{\left( \mu
\right) }$ (the numerator in the Weyl character formula $ch\left( L^{\mu
}\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see
for example \cite{humphreys1997introduction}) the Weyl denominator $R=\Psi _{%
\frak{a}_{\bot }}^{\left( 0\right) }$ and the projection $\Psi _{\left( 
\frak{a},\frak{a}_{\bot }\right) }^{\left( \mu \right) }=\pi _{\frak{a}}%
\frac{\Psi _{\frak{g}}^{\left( \mu \right) }}{\Psi _{\frak{a}_{\bot
}}^{\left( 0\right) }}$. The element $\Psi _{\frak{g}}^{\left( \mu \right) }$
can be decomposed with respect to the set of Weyl numerators $\Psi _{\frak{a}%
_{\bot }}^{\left( \mu \right) }$ of $\frak{a}_{\bot }$. This decomposition
provides the possibility to construct the set of highest weight modules $L_{%
\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. When
the injection \ $\frak{a}_{\bot }\hookrightarrow \frak{g}$ \ satisfies the
''standard parabolic'' conditions these modules give rise to the parabolic
Verma modules $M_{\left( \widetilde{\frak{a}_{\perp }}\hookrightarrow \frak{g%
}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$ so that the initial
character $ch\left( L^{\mu }\right) $ is finally decomposed into the
alternating sum of such. On the other hand when the parabolic conditions are
violated the construction survives and exhibites a decomposition with
respect to a set of Verma modules $M_{\left( \widetilde{\frak{b}_{\perp }},%
\frak{g}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. In such a
situation the algebra $\widetilde{\frak{b}_{\perp }}$ is not a subalgebra in 
$\frak{g}$ but a contraction of $\widetilde{\frak{a}_{\perp }}$.

Some general properties of the proposed decompositions are formulated in
terms of a specific element $\Gamma _{\frak{a}\rightarrow \frak{g}}$ of the
group algebra $\mathcal{E}\left( \frak{g}\right) $ called ''the injection
fan''. Using this tool the simple and explicit algorithm for branching
coefficients computations applicable for an arbitrary (maximal or
nonmaximal) subalgebras of finite-dimensional or affine Lie algebras was
obtained in [our preprint].

@@

Consider the highest weight $\mu \in P^{+}$ of an integrable module $L^{\mu
} $ of $\frak{g}$ and let $\frak{a}\subset \frak{g}$ be a reductive
subalgebra of $\frak{g}$. Let $L^{\mu }$ be completely reducible with
respect to $\frak{a}$, 
\[
L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }. 
\]
Using the projection operator $\pi _{\frak{a}}$ (to the weight space $\frak{%
h_{a}}^{\ast }$) one can rewrite this decomposition in terms of formal
characters: 
\begin{equation}
\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
\label{branching1}
\end{equation}
The module $L^{\mu }$ has the BGG-resolution (see [BGG] and [Humphrys]). All
the members of the filtration sequence are the direct sums of Verma modules
and all their highest weights $\nu $ are strongly linked to $\mu $: 
\[
\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
W\right\} . 
\]

@@

Then the element $\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{%
\af_{\perp }}}\right) $ can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
the singular elements $e^{\mu _{\af}\left( u\right) }$ with the
coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
}}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right) $:
\begin{equation}
\quad \pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af%
_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{\af}\left(
u\right) }\mathrm{\dim }\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
\widetilde{\af_{\perp }}}\left( u\right) }\right) .
\label{eq:11}
\end{equation}
\end{lemma}
This lemma can be used to state the recurrent relation for the branching coefficients for the reduction of $\gf$-module to $\af$-modules. (See \cite{2010arXiv1007.0318L} for the details). It will be also useful for the discussion of special subalgebras. 
\end{corollary}
\begin{corollary}
  \label{corollary-2}
 If $\af, \afb$ are regular subalgebras the simple root system $\alpha_1,\dots, \alpha_r$ of $\gf$ sometimes can be chosen in such a way that simple roots $\beta_1,\dots,\beta_{r_{\afb}}$ of $\afb$ are contained in it. Denote the set of roots $\beta_i$ by $I$. This notation is in the agreement with the book \cite{humphreys2008representations}.
  \begin{equation*}
    I=\{\beta_1,\dots,\beta_{r_{\afb}}\}\subset \{\alpha_1,\dots,\alpha_r\}
  \end{equation*}
  Then the subset $I$ determines not only the subalgebra $\afb$, but also the minimal parabolic subalgebra $\mathfrak{p}_I$, such that $\afb\subset \mathfrak{p}$. Then we can consider the modules of the subcategory $\mathcal{O}^{\mathfrak{p}}$, for example the generalized Verma modules $M_{\mathfrak{p}}^{(\mu)}$. This modules are constructed from the irreducible highest-weight modules $L_{\pf}^{(\mu)}$ as follows
  \begin{equation}
    \label{eq:1}
    M_{\pf}^{(\mu)}=U(\gf)\otimes_{U(\pf)} L^{(\mu)}_{\pf}
  \end{equation}
  Denote by $\tilde R$ the denominator constructed of the positive roots of $\gf$ which are not the roots of $\afb$.
  \begin{equation}
    \label{eq:2}
    \tilde R = \prod_{\alpha\in \Delta^+\setminus \Delta^{+}_{\afb}} \left(1-e^{-\alpha}\right)^{\mathrm{mult}_{\gf} \alpha}
  \end{equation}
If we expand $\frac{1}{\tilde R}$ the coefficients near the terms $e^{\xi}$ are given by the Kostant partition function $p^I$ constructed from the roots of $\gf$ which are not in $I$. 
The character of the generalized Verma module then can be formally written as
\begin{equation}
  \label{eq:3}
  \mathrm{ch} M^{(\mu)}_{\pf}=\frac{1}{\tilde R} \mathrm{ch}L^{(\mu)}_{\pf}
\end{equation}
The character of the irreducible finite-dimensional $\pf$-module $L^{(\mu)}_{\pf}$ differs from the character of the irreducible finite-dimensional $\afb$-module by the factor $e^{\pi_{\tilde\af}(\mu)}$, since $\pf$ contains the full Cartan subalgebra $\hf\subset\gf$.
Now if we multiply the statement (\ref{eq:4}) of the lemma \ref{lemma-1} by $\frac{1}{\tilde R}$ we get the character of irreducible highest-weight module $L^{(\mu)}$ on the left and the sum of the characters of generalized Verma modules on the right-hand side of the equation:
\begin{multline}
  \label{eq:7}
  \mathrm{ch}L^{(\mu)}_{\gf}=
  \sum_{u\in W/W_{\afb}}\epsilon(u)e^{\pi_{\af\oplus\mathfrak{h}_d}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \frac{1}{\tilde R}\mathrm{ch} L_{\afb}^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}=\\
  \sum_{u \in W/W_{\afb}} \epsilon(u) \mathrm{ch} M^{(u(\mu+\rho)-\rho)}_{\pf}
\end{multline}
So we have recovered the Bernstein-Gelfand-Gelfand resolution \cite{bernstein1975differential} for the parabolic category ${\cal O}^{\pf}$.
\end{corollary}

>>>>

To show this we use the recursive approach to branching presented in \cite{2010arXiv1007.0318L} (similar to the one used in \cite{ilyin812pbc} for maximal
embeddings). We consider the subalgebra $\frak{a}$ together with its
counterpart $\frak{a}_{\bot }$ ''orthogonal'' to $\frak{a}$ with respect to
the Killing form and also $\widetilde{\frak{a}_{\perp }}:=\frak{a}_{\perp
}\oplus \frak{h}_{\perp }$ where $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus 
\frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$. For any reductive
algebra $\frak{a}$ the subalgebra $\frak{a}_{\bot }\hookrightarrow \frak{g}$
is regular and reductive. For a highest weight integrable module $L^{\left(
\mu \right) }$ and orthogonal pair of subalgebras $\left( \frak{a},\frak{a}%
_{\bot }\right) $ we consider the singular element $\Psi ^{\left( \mu
\right) }$ (the numerator in the Weyl character formula $ch\left( L^{\mu
}\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see
for example \cite{humphreys1997introduction}) the Weyl denominator $R=\Psi _{%
\frak{a}_{\bot }}^{\left( 0\right) }$ and the projection $\Psi _{\left( 
\frak{a},\frak{a}_{\bot }\right) }^{\left( \mu \right) }=\pi _{\frak{a}}%
\frac{\Psi _{\frak{g}}^{\left( \mu \right) }}{\Psi _{\frak{a}_{\bot
}}^{\left( 0\right) }}$. The element $\Psi _{\frak{g}}^{\left( \mu \right) }$
can be decomposed with respect to the set of Weyl numerators $\Psi _{\frak{a}%
_{\bot }}^{\left( \mu \right) }$ of $\frak{a}_{\bot }$. This decomposition
provides the possibility to construct the set of highest weight modules $L_{%
\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. When
the injection \ $\frak{a}_{\bot }\hookrightarrow \frak{g}$ \ satisfies the
''standard parabolic'' conditions these modules give rise to the parabolic
Verma modules $M_{\left( \widetilde{\frak{a}_{\perp }}\hookrightarrow \frak{g%
}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$ so that the initial
character $ch\left( L^{\mu }\right) $ is finally decomposed into the
alternating sum of such. On the other hand when the parabolic conditions are
violated the construction survives and exhibites a decomposition with
respect to a set of Verma modules $M_{\left( \widetilde{\frak{b}_{\perp }},%
\frak{g}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. In such a
situation the algebra $\widetilde{\frak{b}_{\perp }}$ is not a subalgebra in 
$\frak{g}$ but a contraction of $\widetilde{\frak{a}_{\perp }}$.

Some general properties of the proposed decompositions are formulated in
terms of a specific element $\Gamma _{\frak{a}\rightarrow \frak{g}}$ of the
group algebra $\mathcal{E}\left( \frak{g}\right) $ called ''the injection
fan''. Using this tool the simple and explicit algorithm for branching
coefficients computations applicable for an arbitrary (maximal or
nonmaximal) subalgebras of finite-dimensional or affine Lie algebras was
obtained in \cite{2010arXiv1007.0318L}.

@@

Consider the highest weight $\mu \in P^{+}$ of an integrable module $L^{\mu
} $ of $\frak{g}$ and let $\frak{a}\subset \frak{g}$ be a reductive
subalgebra of $\frak{g}$. Let $L^{\mu }$ be completely reducible with
respect to $\frak{a}$, 
\[
L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }. 
\]
Using the projection operator $\pi _{\frak{a}}$ (to the weight space $\frak{%
h_{a}}^{\ast }$) one can rewrite this decomposition in terms of formal
characters: 
\begin{equation}
\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
\label{branching1}
\end{equation}
The module $L^{\mu }$ has the BGG-resolution (see
\cite{bernstein1976category,bernstein1975differential,bernstein1971structure} and \cite{humphreys2008representations}). All
the members of the filtration sequence are the direct sums of Verma modules
and all their highest weights $\nu $ are strongly linked to $\mu $: 
\[
\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
W\right\} . 
\]

@@

Then the element $\pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{%
\af_{\perp }}}\right) $ can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
the singular elements $e^{\mu _{\af}\left( u\right) }$ with the
coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\af_{\perp
}}}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right) $:
\begin{equation}
\quad \pi _{\af}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\af%
_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{\af}\left(
u\right) }\mathrm{\dim }\left( L_{\widetilde{\af_{\perp }}}^{\mu _{%
\widetilde{\af_{\perp }}}\left( u\right) }\right) .
\label{eq:11}
\end{equation}
\end{lemma}
This lemma can be used to state the recurrent relation for the branching coefficients for the reduction of $\gf$-module to $\af$-modules. (See \cite{2010arXiv1007.0318L} for the details). It will be also useful for the discussion of special subalgebras. 
\end{corollary}
\begin{corollary}
  \label{corollary-2}
 If $\af, \afb$ are regular subalgebras the simple root system $\alpha_1,\dots, \alpha_r$ of $\gf$ sometimes can be chosen in such a way that simple roots $\beta_1,\dots,\beta_{r_{\afb}}$ of $\afb$ are contained in it. Denote the set of roots $\beta_i$ by $I$. This notation is in the agreement with the book \cite{humphreys2008representations}.
  \begin{equation*}
    I=\{\beta_1,\dots,\beta_{r_{\afb}}\}\subset \{\alpha_1,\dots,\alpha_r\}
  \end{equation*}
  Then the subset $I$ determines not only the subalgebra $\afb$, but also the minimal parabolic subalgebra $\mathfrak{p}_I$, such that $\afb\subset \mathfrak{p}$. Then we can consider the modules of the subcategory $\mathcal{O}^{\mathfrak{p}}$, for example the generalized Verma modules $M_{\mathfrak{p}}^{(\mu)}$. This modules are constructed from the irreducible highest-weight modules $L_{\pf}^{(\mu)}$ as follows
  \begin{equation}
    \label{eq:1}
    M_{\pf}^{(\mu)}=U(\gf)\otimes_{U(\pf)} L^{(\mu)}_{\pf}
  \end{equation}
  Denote by $\tilde R$ the denominator constructed of the positive roots of $\gf$ which are not the roots of $\afb$.
  \begin{equation}
    \label{eq:2}
    \tilde R = \prod_{\alpha\in \Delta^+\setminus \Delta^{+}_{\afb}} \left(1-e^{-\alpha}\right)^{\mathrm{mult}_{\gf} \alpha}
  \end{equation}
If we expand $\frac{1}{\tilde R}$ the coefficients near the terms $e^{\xi}$ are given by the Kostant partition function $p^I$ constructed from the roots of $\gf$ which are not in $I$. 
The character of the generalized Verma module then can be formally written as
\begin{equation}
  \label{eq:3}
  \mathrm{ch} M^{(\mu)}_{\pf}=\frac{1}{\tilde R} \mathrm{ch}L^{(\mu)}_{\pf}
\end{equation}
The character of the irreducible finite-dimensional $\pf$-module $L^{(\mu)}_{\pf}$ differs from the character of the irreducible finite-dimensional $\afb$-module by the factor $e^{\pi_{\tilde\af}(\mu)}$, since $\pf$ contains the full Cartan subalgebra $\hf\subset\gf$.
Now if we multiply the statement (\ref{eq:4}) of the lemma \ref{lemma-1} by $\frac{1}{\tilde R}$ we get the character of irreducible highest-weight module $L^{(\mu)}$ on the left and the sum of the characters of generalized Verma modules on the right-hand side of the equation:
\begin{multline}
  \label{eq:7}
  \mathrm{ch}L^{(\mu)}_{\gf}=
  \sum_{u\in W/W_{\afb}}\epsilon(u)e^{\pi_{\af\oplus\mathfrak{h}_d}\left[(u(\mu+\rho)-\rho)\right]+\mathcal{D}}\cdot \frac{1}{\tilde R}\mathrm{ch} L_{\afb}^{\piab(u(\mu+\rho)-\rho)-\mathcal{D}}=\\
  \sum_{u \in W/W_{\afb}} \epsilon(u) \mathrm{ch} M^{(u(\mu+\rho)-\rho)}_{\pf}
\end{multline}
So we have recovered the Bernstein-Gelfand-Gelfand resolution \cite{bernstein1976category,bernstein1975differential,bernstein1971structure} for the parabolic category ${\cal O}^{\pf}$.
\end{corollary}
